### 2023-06-16 resilience-safe-up.tex
up

\subsection{Case: $\Bad=\downarrow \Bad$ and $\Safe=\uparrow \Safe$.}

@@

We start with the case $\Bad=\downarrow \Bad$ and $\Safe=\uparrow \Safe$. 
It can be viewed as a generalizeation
 of coverability, namely,
it asks whether for every element of $\Bad$ it is possible to cover an element of the basis of $\Safe$.

@@

Without the completion-post-effective hypothesis or the pred-basis hypothesis, coverability 
becomes undecidable. For instance the coverability problem for strongly increasing well-structured nets is undecidable~\cite{FMP-ic04}. 
Coverability reduce
to resilience when $\Bad = \downarrow \Bad$ and  $\Safe = \uparrow \Safe$,
as $s \to^* \uparrow t$ 
reduces to $(\Safe,\Bad)$-resilience for $\Bad = \downarrow s$ and $\Safe = \uparrow t$.
Hence, without the completion-post-effective hypothesis, 
{\sc Resilience} itself is undecidable.

>>>>

\subsection{Case: $\Safe=\uparrow \Safe$.}

@@

We start with the case $\Bad=\downarrow \Bad$ and $\Safe=\uparrow \Safe$. 
It can be viewed as a generalizeation
 of coverability, as
it asks whether for every element of $\Bad$ it is possible to cover an element of the basis of $\Safe$.

@@

Without the completion-post-effective hypothesis nor the pred-basis hypothesis, coverability 
becomes undecidable. For instance the coverability problem for strongly increasing well-structured nets is undecidable~\cite{FMP-ic04}. 
Coverability reduce
to resilience when $\Bad = \downarrow \Bad$ and  $\Safe = \uparrow \Safe$,
as $s \to^* \uparrow t$ 
reduces to $(\Safe,\Bad)$-resilience for $\Bad = \downarrow s$ and $\Safe = \uparrow t$.
Hence, without the completion-post-effective hypothesis, 
{\sc Resilience} itself is undecidable.

Remark we did not make use of the hypothesis that $\Bad$ is the complement of $\Safe$, simply using
$\Bad=\downarrow \Bad$ and $\Safe=\uparrow \Safe$, thus 
the above results still hold in the more general case where $\Bad$ and $\Safe$ are not complements of each others.
